Clustering in a hyperbolic model of complex networks.

### 2019-02-21 clustering_infinite_model.tex
no more \Delta in Section 3

&\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 

@@

\Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)

@@

Therefore, the desired value of $\lim_{\alpha \rightarrow 1} \Delta_{\Pcal_{\alpha,\nu}}(y_0(z_0))$ is given by

@@

Instead of extracting the scaling of $\gamma(k)$ from its explicit expression, it turns out to be more convenient to derive it directly. Recall that
\[
	\gamma(k) = \frac{\int_0^\infty \rho(y,k) P(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
\]
The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
\[
	\int_0^{\infty} P(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
\]
and in particular the function $P(y)$. We therefore start with establishing the asymptotic behavior of the latter.

@@

Now we will proof all other cases with $\alpha > 3/4$. For simplicity we write
\[
	Q_\alpha := \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
		+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}.
\]
Then, by Lemma~\ref{lem:Paneq1} we get
\begin{align*}
	e^{y/2} P(y) &= \frac{\alpha - \frac{1}{2}}{\alpha - 1} 
		+ \frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right)\\
	&\hspace{10pt}- e^{-(4\alpha - 3)\frac{y}{2}}\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}\\
	&\hspace{10pt}+ e^{-(4\alpha - 3)\frac{y}{2}}Q_\alpha + \frac{(\alpha-\frac{1}{2})^2}{4(\alpha-1)^2} e^{-\frac{y}{2}}.
\end{align*}
The first term is constant while the last two terms go to zero as $y \to \infty$. We will therefore focus on the remain two terms. For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary} 
\[
	\frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right) 
	\sim \frac{-2\alpha}{8(\alpha - 1)\alpha} = -\frac{1}{4(\alpha -1)},
\]
as $y \to \infty$. Finally, writing $z = e^{-\frac{y}{2}}$ we get that
\[
	e^{-(4\alpha - 3)\frac{y}{2}} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)
	= z^{4\alpha - 3} B^-(1 - z, 2 \alpha, 3 - 4 \alpha).
\]
Therefore it follows, see Lemma~\ref{lem:asymptotics_incomplete_beta}, that
\begin{align*}
	\lim_{y \to \infty} - e^{-(4\alpha - 3)\frac{y}{2}}
		\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	&= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}\\
	&= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
\end{align*}
We conclude that as $y \to \infty$
\begin{align*}
	e^{y/2} P(y) 
	&\sim \frac{\alpha - \frac{1}{2}}{\alpha - 1} -\frac{1}{4(\alpha -1)} - \frac{1}{4(\alpha - 1)(4\alpha - 3)}
	= \frac{1 - 3\alpha + 2 \alpha^2}{(\alpha - 1)(\alpha - \frac{3}{4})} 
	= \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}},
\end{align*}
which finishes the proof.
\end{proof}

>>>>

&P(y_0(z_0)) = \frac{1}{\alpha-1}\left( \sum_{i\in \{1,2,5,6,7\}} s_i(1)+\sum_{i\in\{1,2,5,6,7\}} 

@@

P(y_0(z_0)) = \sum_{i \in\{1,2,5,6,7\}} s_i'(1)+\frac{1}{2}(s_3''(1)+s_4''(1)) + o(1)

@@

Therefore, the desired value of $\lim_{\alpha \rightarrow 1} P(y_0(z_0))$ is given by

@@

Instead of extracting the scaling of $\gamma(k)$ from its explicit expression, it turns out to be more convenient to derive it directly. Recall that
\[
	\gamma(k) = \frac{\int_0^\infty \rho(y,k) P(y) \alpha e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}.
\]
The asymptotic behavior for the denominator follows from~\eqref{eq:degree_distribution_P_asymptotics}. Hence, the main term to consider is the numerator
\[
	\int_0^{\infty} P(y) \, \rho(y,k) \alpha e^{-\alpha y} \, dy,
\]
and in particular the function $P(y)$. We therefore start with establishing the asymptotic behavior of the latter. First we combine~\eqref{eq:degree_distribution_P_asymptotics} and~\eqref{eq:general_integral_rho_y_k} to obtain the following scaling result
\begin{equation}\label{eq:general_clustering_integral_scaling}
	\frac{\int_0^\infty e^{-\beta y} \rho(y,k) \alpha e^{-\alpha y} \dd y}
	{\int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \dd y}
	\sim \xi_{\alpha, \nu}^{2\beta} k^{-2\beta}.
\end{equation}

@@

Now we will deal with the case $\alpha > 3/4$ and $\alpha \not = 1$. For simplicity we write
\[
	Q_\alpha := \frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} 
		+ \frac{(\alpha - 1/2 ) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)}{2(\alpha - 1) \alpha}.
\]
Then, by Lemma~\ref{lem:Paneq1} we get
\begin{align*}
	e^{y/2} P(y) &= \frac{\alpha - \frac{1}{2}}{\alpha - 1} 
		+ \frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right)\\
	&\hspace{10pt}- e^{-(4\alpha - 3)\frac{y}{2}}\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}\\
	&\hspace{10pt}+ e^{-(4\alpha - 3)\frac{y}{2}}Q_\alpha + \frac{(\alpha-\frac{1}{2})^2}{4(\alpha-1)^2} e^{-\frac{y}{2}}.
\end{align*}
The first term is constant while the last two terms go to zero as $y \to \infty$. We will therefore focus on the remaining two terms. For the first we have, see~\eqref{eq:asymptotics_Delta_P_auxiliary} 
\[
	\frac{e^{\frac{y}{2}}}{8(\alpha - 1)\alpha}\left(\left(1 - e^{-\frac{y}{2}}\right)^{2\alpha}-1\right) 
	\sim \frac{-2\alpha}{8(\alpha - 1)\alpha} = -\frac{1}{4(\alpha -1)},
\]
as $y \to \infty$. Finally, writing $z = e^{-\frac{y}{2}}$ we get that
\[
	e^{-(4\alpha - 3)\frac{y}{2}} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)
	= z^{4\alpha - 3} B^-(1 - z, 2 \alpha, 3 - 4 \alpha).
\]
Therefore it follows, see Lemma~\ref{lem:asymptotics_incomplete_beta}, that
\begin{align*}
	\lim_{y \to \infty} - e^{-(4\alpha - 3)\frac{y}{2}}
		\frac{B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	&= \lim_{z \to 0} z^{4\alpha - 3} \frac{B^-(1 - z, 2 \alpha, 3 - 4 \alpha)}{4(\alpha - 1)}\\
	&= \frac{1}{4(\alpha - 1)(4\alpha - 3)}.
\end{align*}
We conclude that as $y \to \infty$
\begin{align*}
	e^{y/2} P(y) 
	&\sim \frac{\alpha - \frac{1}{2}}{\alpha - 1} -\frac{1}{4(\alpha -1)} - \frac{1}{4(\alpha - 1)(4\alpha - 3)}
	= \frac{1 - 3\alpha + 2 \alpha^2}{(\alpha - 1)(\alpha - \frac{3}{4})} 
	= \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}},
\end{align*}
which finishes the proof.
\end{proof}
